\documentclass[a4paper,11pt]{article}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage[ruled]{algorithm2e}
\usetikzlibrary{arrows}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}[section]
\newtheorem*{remark}{Remark}
\newtheorem{proposition}[theorem]{Proposition}
\begin{document}

\section{Goal}
The goal is to delineate the distinct eras of each NBA franchise. Taking a player-centric approach, this is equivalent to determining which players define the history of each franchise. I've chosen to quantify a player's worth based on his win share\footnote{A measure that tries to quantify how many regular-season wins an individual accounted for. Complete explanation \href{http://www.basketball-reference.com/about/ws.html}{here}.} percentage\footnote{Simply calculated by dividing an individual's win shares by the sum of the win shares of all members of his team.} (WS\%), because a player with a large percentage of his team's win shares in a given season is likely to be crucial to that era of the franchise. Other metrics could be used to gain different perspectives on a team's history.

The method used to select these ``franchise-definers'' should keep the number of chosen players to a minimum, in order to weed out those who were not true flagships of any particular era. But of course, the obvious superstar players should not be excluded either.

\section{Method}
Consider an arbitrary team $X$. We would like to determine the set of franchise-defining players for $X$. Let:\\

$P_j=$ the set of players on team $X$ in season $j$.\\ 


$w_j(p) = \left\{ \begin{array}{ll}
		            \text{WS\% of player } p \text{ in season } j & \quad p \in P_j\\
		            0 & \quad \text{otherwise}
		        \end{array}
 		   \right. $\\



As a preprocessing step, I use the following algorithm to exclude a number of players that clearly did not have a high enough impact:\\

	\begin{algorithm} [H]
	\caption{Preprocess($T$)}
	\For{each season $j$} {
		Sort $P_j$ in descending order of WS\%\;
	$V^\prime := V^\prime \cup \{v^\prime\}$\;
       	\For{each $u \in V$ such that $(u,v) \in E$ (undirected)} {
	$E^\prime := E^\prime \cup (u,v^\prime)$\;
	}
	}
	return ($G^\prime,k+1$)\;
	\end{algorithm}


To make the problem more tractable and interesting, I impose the following constraints:

\begin{enumerate}
\item $\forall_j \; P_j \ne \emptyset$ \footnote{I do this because it means JaVale McGee could possibly show up on the Wizard's list of franchise-definers. Unsuccessful eras of franchises need to be remembered, and I never want to forget JaVale's stint in Washington.}.
\item $\forall_j  \; \sum_{p \in P} w_j(p) \ge t$, where $t$ is a tweakable parameter
\end{enumerate}

Taking that one step further: to ascertain that every season is well-represented, I'll select FDs in a way that ensures $t\%$ of the total win shares are accounted for each season, where $t$ is a tweakable parameter. 



\section{IP-Formulation}

$r_{ij} = \left\{ \begin{array}{ll}
		            1 & \quad \text{reign } i \text{ is selected}\\
		            0 & \quad \text{otherwise}
		        \end{array}
 		   \right. $
\\
\\
$w_{ij} = \left\{ \begin{array}{ll}
		            \text{WS\% of player in reign } i \text{ during season } j & \quad j \in R_i\\
		            0 & \quad \text{otherwise}
		        \end{array}
 		   \right. $



\end{document}